We considered available data in some open sources 
related to the defect detection problem. Some datasets 
have only code samples and labels, while others have 
calculated some code metrics.

ETH JavaScript Dataset\footnote{\url{https://www.sri.inf.ethz.ch/js150}}
includes 150,000 JavaScript code samples represented as AST trees. 
The dataset has been used in a binary classification task. 
Target positive examples were extracted from the code 
and negative examples were generated using 
Negative Sampling techique. The dataset 
was used by~\citet{DeepBugs} in an attempt to find the following defects: 
swapped arguments, wrong binary operator, and wrong binary operand.

NASA Dataset\footnote{\url{http://promise.site.uottawa.ca/SERepository/datasets-page.html}}
includes 20 small-sized datasets (20 to 2000 samples in each one) of NASA projects. 
It does not contain code itself but only code metrics. The data 
was previously used for defect prediction, cost estimation, successful reuse, and requirements tracing.
 
Defects4j Dataset\footnote{\url{https://github.com/rjust/defects4j/tree/additional-projects-4}}
includes code samples from different projects, 
where each one has 52 defects of different 
type. The datasets was built by scrapping bug reports and commits 
that fixed them. This dataset does not have labels.

BugLocalization Dataset:\footnote{\url{https://github.com/yanxiao6/BugLocalization-dataset/tree/master/dataset}}
has 18,500 Java defect report samples from five GitHub-hosted projects. 
Each sample consists of defect description, a commit to fix the defect 
and a link to GitHub source code file.

CodeSearchNet dataset:\footnote{\url{https://github.com/github/CodeSearchNet}}
is a large dataset of over two million rows of code 
collected from open source libraries. The dataset contains 
Python, Javascript, Ruby, Go, Java, and PHP languages. 
Each sample consists of a function code and a comment related 
to the function. The dataset is built for a semantic code search task.
