% SPDX-FileCopyrightText: Copyright (c) 2019-2026 Aibolit
% SPDX-License-Identifier: MIT

Aibolit is a recommender system that helps improve the quality of Java classes.
The recommendations are learned from OSS Java projects using ML methods.
Aibolit provides ranked recommendations for each specific Java class,
which differentiates Aibolit from other style checkers and makes it unique.

Aibolit is an extendable system, allowing anyone to add new patterns and to
increase the training dataset, and thus improve the precision and usefulness
of recommendations. Aibolit can also be used as a framework for analysis of
patterns and to decide whether any pattern, however subjective it is, is an anti-pattern or a pro-pattern
with respect to a particular quality metric. As a complementary result,
we contribute a 100K+ dataset of patterns and metrics calculated for Java classes.

The first version of Aibolit is relatively simple and there is room
for improvement. If an anti-pattern is found, we recommend fixing all instances
of the pattern in the code. Instead, we may consider each specific occurrence of the pattern.
We may exploit its relative position in the structure of the code, rather than just counting
the frequency. Moreover, Aibolit inspects each Java class independently, but
we might consider the relations between classes in the future. Furthermore,
Aibolit's prediction model relies on patterns only. In order to improve the model,
we have to think about additional features, for example, information about
the project domain or used frameworks.

Aibolit is a firm step toward the next generation of tools to control
and improve software quality. It is a complementary tool for
product owners who already use tools to manage software quality.
